Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-14 astronum_2017/astronum-amrex.tex
typo

Our suite of application codes is built on the
\amrex\ block-structured adaptive mesh refinement (AMR) library.  The
basic programming model has \amrex\ managing the grid data-structures
and parallel communications, and it calls the computational kernels on
a patch-by-patch basis.  The core library is written in \cpp\ with the
computational kernels written in Fortran\footnote{Currently
  \maestro\ is using an older pure-Fortran interface, but this will be
  ported to the \cpp\ AMReX this coming year.}---this allows us to take
advantage of the strengths of both languages.AMReX supports subcycling
in time, which we use in \castro.

>>>>

Our suite of application codes is built on the
\amrex\ block-structured adaptive mesh refinement (AMR) library.  The
basic programming model has \amrex\ managing the grid data-structures
and parallel communications, and it calls the computational kernels on
a patch-by-patch basis.  The core library is written in \cpp\ with the
computational kernels written in Fortran\footnote{Currently
  \maestro\ is using an older pure-Fortran interface, but this will be
  ported to the \cpp\ \amrex\ this coming year.}---this allows us to take
advantage of the strengths of both languages. \amrex\ supports subcycling
in time, which we use in \castro.
